---
title: "PARP Analysis of ABT-263 Anti-Fibrotic Therapy"
author: "Stephen G. Collins and Peter Higgins"
output:
  word_document: default
  pdf_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
library(ggsignif)
library(readxl)
library(here)
```


### Read in data 


```{r echo=FALSE, message=FALSE, warning=FALSE}

parpdata <- read_excel(here::here("ABT-263_Invitro_Expt_SGC.xlsx"),
                        sheet = "apop_prot")
parpdata %>% 
  select(grp...37, parp_norm_gapdh...41) %>% 
  filter(!is.na(grp...37)) ->
parpdata

names(parpdata) <- c("Group", "PARP")

parpdata %>% 
  mutate(PARP = as.numeric(PARP),
         Group = as.factor(Group),
         fasl = case_when(Group %in% 2:5 ~ 1,
                          TRUE ~ 0),
         abt = case_when(Group %in% 3:6 ~ 1,
                          TRUE ~ 0))->
parpdata

labels = c("Untreated", "Fas\nLigand", "FasL +\n100 nM\nABT-263",
           "FasL +\n300 nM\nABT-263", "FasL +\n1000 nM\nABT-263",
           "1000 nM\nABT-263")

parpdata$Group <- ordered(parpdata$Group,
levels = c(1,2,3,4,5,6),
labels = labels)


```




### Plot the PARP data for powerpoint 


```{r echo=FALSE, fig.cap = "ABT-263 Cleaved PARP", fig.height=4, fig.width=6}
parpdata %>% 
  ggplot(aes(x=Group, y=PARP)) +
  geom_boxplot(outlier.size = -1, color="gray35") +
  geom_jitter(width = 0.16, size=2, shape=21, stroke=1.2) +
  labs(title = "Cleaved PARP Induction by ABT-263\nin Intestinal Myofibroblasts",
       caption = "Incubated for 24 hours with FasL and ABT-263,\nMeasurement by Western Blot") +
  theme_bw(base_size = 16) +
  ylab("Cleaved PARP/\nGADPH Ratio") +
  xlab("Treatment Group") +
  theme(legend.position = 'none')

ggsave(here('parp.png'))
  

```

### Labeling 
Let's talk about labeling axes.

this is done with the _labs()_ function.
Add it on to your plot with a + at the end of a line
then labs() with several arguments within the parentheses.
These can include
- title = "Title"
- x = "x axis label"
- y = "y axis label"
- subtitle = "This goes below the title"
- caption = "This goes below the plot"
- tag = "A - this goes in top left, to label a panel in a multi-panel plot"

You can remove a label by setting it equal to null.

If you have a legend, you can change the title of the legend by setting this in labs.

- labs(color = "TGFb Treatment", shape = "ABT263 dose")

### Color mapping
You can map to a fixed color within ggplot or within a geom.
The color must be in quotes, because it is not an object in the environment.
For example, color = "maroon".

You can map to a color determined by a variable, without quotes (because the variable is an object in the environment), but it has to be within the aes() function within either ggplot or a geom.

The geoms 'inherit' aes mappings from ggplot, unless you over-write them in the geom.

### line breaks in labels
You can create a line break within a quoted label by inserting "\n"
which calls for a new line.
Try inserting a few line breaks into labels

```{r edited plot}
parpdata %>% 
  ggplot(aes(x=Group, y=PARP, color = as.factor(abt))) +
  geom_boxplot(outlier.size = -1, color="maroon") +
  geom_jitter(width = 0.16, size=2, shape=21, stroke=1.2) +
  labs(title = "Cleaved PARP Induction by ABT-263\nin Intestinal Myofibroblasts",
       caption = "Incubated for 24 hours with FasL and ABT-263,\nMeasurement by Western Blot",
       tag = "A",
       y = "Cleaved PARP/GADPH Ratio",
       x = "Treatment Group") +
  theme_bw(base_size = 16) +
  labs(color = "ABT") +
  theme(legend.position = "bottom",  #top, left, none, right
        plot.tag.position = "topright") +
  theme(legend.position = c(0.85, 0.6)) + 
  geom_signif(comparisons = list(c(2,3)), y_position = 2.3, color="black") +
  theme(legend.background = element_rect(color="black",
                                         fill = "lightblue"))

```


